Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-23 cordillera-cycle.tex
Rev. Marshall: fixed climate patterns.

      The westerly position of the modelled ice divide and western ice sheet
      margin may also reflect the fact
      that our model does not include feedback mechanisms between ice sheet
      topography and the regional climate. Firstly, during the build-up
      phase preceding the LGM, rapid accumulation over the Coast Mountains
      enhanced the topographic barrier formed by these mountain ranges,
      which likely resulted in a~decrease of precipitation and, therefore,
      a~decrease of accumulation in the interior. Secondly, latent warming
      of the moisture-depleted air parcels flowing over this enhanced
      topography could have resulted in an inflow of potentially warmer air
      over the eastern flank of the ice sheet, increasing melt along the
      advancing margin \citep[cf.][]{Langen.etal.2012}. Because these two
      processes, both with a~tendency to limit ice-sheet growth, are absent
      from our model, the eastern margin of the ice sheet and the position
      of the main meridional ice divide are certainly biased towards the
      east in our simulations \citep{Seguinot.etal.2014}.

>>>>

      The westerly position of the modelled ice divide and western ice sheet
      margin may also reflect the fact that our model assumes fixed
      modern-day spatial patterns for temperature and precipitation and thus
      does not include feedback mechanisms between ice sheet topography and
      the regional climate. Regarding temperature, it is reasonable to think
      that the cooling was greater inland than near the coast, prohibiting
      melt at the western margin. However, our simulations already produce
      an excess of ice inland. Including such a temperature continentality
      gradient in the model while keeping the precipitation pattern constant
      would thus cause an even greater mismatch between the model results
      and the geologically reconstructed Last Glacial Maximum (LGM) ice
      margins.

      Consequently, the mismatch we observe between the modelled and
      reconstructed LGM ice margins let us think that the assumption of
      fixed modern-day precipitation patterns is more critical than the
      assumption of fixed modern-day temperature patterns.
      Firstly, during the build-up
      phase preceding the LGM, rapid accumulation over the Coast Mountains
      enhanced the topographic barrier formed by these mountain ranges,
      which likely resulted in a~decrease of precipitation and, therefore,
      a~decrease of accumulation in the interior. Secondly, latent warming
      of the moisture-depleted air parcels flowing over this enhanced
      topography could have resulted in an inflow of potentially warmer air
      over the eastern flank of the ice sheet, counterbalancing the potential
      continentality gradient discussed above through increasing melt along the
      advancing margin \citep[cf.][]{Langen.etal.2012}. Because these two
      processes, both with a~tendency to limit ice-sheet growth, are absent
      from our model, the eastern margin of the ice sheet and the position
      of the main meridional ice divide are certainly biased towards the
      east in our simulations \citep{Seguinot.etal.2014}.
